\chapter{Business Analysis}
\section{Problem}
Home owners who are in possession of excess floor space in the form of unused rooms or annexes to their homes) could capitalize on the major increase in human traffic across all the borders of the European Union\footnote{Add a reference to this increase. here you can place the stats used in the flights of europe} as well as internally of each country in Europe by offering these travelers short term accomodation at a "reasonable" or suitable rate for both the traveler and the owner. The problem for such home owners is the extra overhead costs spent in advertising costs and/or other third parties(from here on referred to as "third parties") that help facilitate these transfers. Sometimes the costs are too large for smaller owners to handle and thus they lose their share of the market as well as their share of the total revenue spent on accomodation by the above mentioned traveler.\\
In the same way the European traveler who is experiencing a squeeze in income is looking for cheaper accomodation and yet keeping the same or similar standard of accomodation as previously when spending was not so limited. 

\section{Existing Solutions}
There is a range of solutions available for the home owner to make use of. An example of an existing solution is Airbnb(http://airbnb.com), which offers users an opportunity to rent out a house from someone else. A popular site in Poland is booking.pl(http://www.booking.pl) which allows users to search for accomodation in a private house. 

These existing solutions don't offer one group of users, that is the owners of homes, a way to comment the stay of their clients and thus enabling other home owners to in some way mitigate unwanted customers(i.e destructive, not following policy etc) but at the same time limit the ad hoc discrimination of these same customers. The existing solutions don't offer the client an opportunity to swap his/her reservation with another client for what ever reason but rather charge penalty fees so as to discourage such behaviour. 

